\LARGE \bf Approximately Orchestrated Road Traffic Automata\\ a General Traffic Simulation Framework

### 2012-03-13 papers/itsc_2012/final.tex
added some comments to Section V

AORTA uses microscopic simulation, modeling individual drivers as agents.
Simulation is discrete-time, meaning an agent accelerates at a fixed rate for
the duration of a ``step'' to achieve a new position and velocity, and
space-continuous, meaning roads are not tiled. The step duration $dt$ is fixed,
enabling agents to reason about collision avoidance and satisfying other
constraints. Setting this value to the average ``reaction time'' of a human
driver may be appropriate for some experiments. Each step, the simulation
does the following:

\begin{enumerate}
  \item Introduces new agents into the map
  \item Updates the position and velocity of agents based on their choice of
  acceleration in the previous step
  \item Checks for collisions
  \item Allows each agent to choose a reaction for the next step
\end{enumerate}

Agents have a few enforced constraints -- they cannot exceed their physical
acceleration capabilities, travel in reverse, or travel past the end of a
traversable without appearing on the next. Intersection policies and avoiding
collisions on the same traversable provide the other constraints, but the
agent's behavior is responsible for obeying these. There are three main components of the
simulation, each configurable by extending built-in implementations of an
interface: agent behaviors, routing strategies, and intersection policies.

Currently agents cannot switch lanes. AORTA allows merging lanes by
treating the merge point as an intersection.

@@

To introduce new agents into the simulation in real-time, users can create
\emph{generators} programatically or using the UI. A generator picks a random
starting position and goal from two sets of roads. Users can select these roads 
by mouse with a bounding polygon in the UI, allowing specific traffic patterns
like rush-hour scenarios to be easily simulated. A generator
may also cover the entire map, uniformly distributing traffic everywhere.

Every step, a generator creates some number of new agents. If the agent's route
policy needs computation like pathfinding to operate, the generator either
performs it immediately (incurring a delay in simulation if it is running) or
sends it to a pool of worker threads to process in the background.

Once an agent's route is ready, the agent waits alongside its starting lane (as
if it is in a driveway or parking lot). When the lane has no agents that could
potentially crash with the new vehicle, the new agent enters the system with
zero initial speed.  Because behaviors must enforce speed limit along a lane 
from the moment an agent enters a road, it is safe for a new agent to enter a road
if there is no other agent within the worst-case distance (traveling distance at the
speed limit, plus stopping distance from this speed) preceeding the spawn point.
To avoid predicting which agents might enter the lane in the near future, there
is a buffer space at the beginning of the lane where a new agent may never
spawn. This disqualifies some short lanes from being spawn points, but this is
not a big limitation in practice.

>>>>

AORTA uses microscopic simulation, modeling individual drivers as agents.
Simulation is discrete-time, meaning an agent accelerates at a fixed rate for
the duration of a ``step'' to achieve a new position and velocity, and
space-continuous, meaning roads are not tiled \commentpk{recommend breaking up
preceding sentence into 2. I lost track haflway}. The step duration $dt$ is
fixed, enabling agents to reason about collision avoidance and satisfying other
constraints \commentpk{preceding sentence is unclear}. Setting this value to
the average ``reaction time'' of a human driver may be appropriate for some
\commentpk{"human driver" instead of some?} experiments. Each step, the
simulation does the following:

\begin{enumerate}
  \item Introduces new agents into the map
  \item Updates the position and velocity of agents based on their choice of
  acceleration in the previous step
  \item Checks for collisions
  \item Allows each agent to choose a reaction \commentpk {should be action} for the next step
\end{enumerate}

Agents have a few enforced constraints -- they cannot exceed their physical
acceleration capabilities, travel in reverse, or travel past the end of a
traversable without appearing on the next. Intersection policies and avoiding
collisions on the same traversable provide the other constraints, but the
agent's behavior is responsible for obeying these \commentpk{if these "other"
constraints are not enforced, clearly specify. Something like "Agent behaviors
are responsible for following intersection policies as directed by an
intersection, and are responsible for not colliding with other agents" probably
sounds a bit better}. There are three main components of the simulation, each
configurable by extending built-in implementations of an interface: agent
behaviors, routing strategies, and intersection policies.

Currently agents cannot switch lanes. AORTA allows merging lanes by treating
the merge point as an intersection. \commentpk{i take it this is an orphan
paragraph?}

\commentpk{this section is a bit incoherent, and might need to be reorganized.
should the constraints be mentioned here explicitly, or maybe just added to
agent behaviors? What are you introducing in the next few subsections? I can
see A-E working together as an explanation of the workings of the simulator,
and would make more sense right after the enumeration above. Section G can be
moved into the experiments section. Once you are done with this primary
explanation, Section F should be talked about separately under something along
the lines of current limitations of the simulator.}

@@

To introduce new agents into the simulation in real-time, users can create
\emph{generators} programatically or using the UI. A generator picks a random
starting position and goal from two sets of roads \commentpk{preceding sentence
is ambiguous, maybe go with "The generator produces a desired amount of traffic
by initializing agents from random locations inside a \textit{start} polygon to
random destinations inside a \textit{goal} polygon, as demarcated by the
user"}. Users can select these roads by mouse with a bounding polygon in the
UI, allowing specific traffic patterns like rush-hour scenarios to be easily
simulated.  A generator \commentpk{polygon} may also cover the entire map,
uniformly distributing traffic everywhere.

Every step, a generator creates some number of new agents. If the agent's route
policy needs computation like pathfinding to operate, the generator either
performs it immediately (incurring a delay in simulation if it is running) or
sends it to a pool of worker threads to process in the background \commentpk{if multiple threads are available?}.

Once an agent's route is ready, the agent waits alongside its starting lane (as
if it is in a driveway or parking lot). When the lane has no agents that could
potentially crash with the new vehicle, the new agent enters the system with
zero initial speed.  Because behaviors must enforce speed limit along a lane
from the moment an agent enters a road, it is safe for a new agent to enter a
road if there is no other agent within the worst-case distance (traveling
distance at the speed limit, plus stopping distance from this speed) preceeding
the spawn point.  To avoid predicting which agents might enter the lane in the
near future, there is a buffer space at the beginning of the lane where a new
agent may never spawn. This disqualifies some short lanes from being spawn
points, but this is not a big limitation in practice. \commentpk{I understand
your concern about explaining the entire methodology, but the last 2 lines are
unnecessary and somewhat distracting}
